CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-16 paper/ms.tex
Add figure 6 in Appendix for diagnostic step

 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.

@@

>>>>

 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
 \bigskip

@@

Randomly choose four stars and manually set their a, b and c equal to parameters in figure 8, then plot the spectrum. The difference between a and c is about 0.3.

\includegraphics[width=170mm]{d_figure_3.png}
\bigskip

\centerline{Fig.3 Comparison of the spectrum}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
\bigskip

Randomly choose four stars and manually set a = 0.7 b = 0.2 c = 0.1, then plot the spectrum. The difference between a and c is 0.6.

\includegraphics[width=170mm]{d_figure_4.png}
\bigskip

\centerline{Fig.4 Comparison of the spectrum}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
\bigskip

Randomly choose four stars and manually set a = 2 b = -2 c = 1, then plot the spectrum. The difference between a and c is 1.

\includegraphics[width=170mm]{d_figure_5.png}
\bigskip

\centerline{Fig.5 Comparison of the spectrum}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
\bigskip

Diagnostic. The parameters showed in figure 6 are the parameters obtained from the optimization process using labels from the APOGEE team, which is not correct. But the parameters to generate optimized flux are from the optimization process using labels from the Cannon, which should be correct.

\includegraphics[width=170mm]{d_figure_6.png}
\bigskip

\centerline{Fig.6 Comparison of the spectrum}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized }
\bigskip
